\chapter{
  Introduction
  (V0.0)
 }

\draftnote{green}{Structure}{
	\begin{enumerate}
		\item What is artificial intelligence?
		\item What is representation learning?
		\item
	\end{enumerate}
}

\draftnote{blue}{About this thesis}{
	\begin{enumerate}
		\item We will introduce the necessary preliminaries as we go rather.
		\item Description of how the work was carried out.
	\end{enumerate}
}


\paragraph{Include: About this thesis.}
When explaining a work of this length, understanding how the work was carried out can help explain why certain decisions were made and particular directions taken.

Initially, our aim was to extend work on Symmetry-based disentangled representation learning [citations] to more general
In particular, we felt that their derivation of the equivariance principle should

We also felt that the language Category Theory seemed like an ideal candidate for describing the structure of an agent's representations because...

A discussion with Hugo Caselles-Dupré about his work in [citations] where he explained "we couldn't figure out how to deal with walls" was particularly insightful.

Our plan was


Distilling thoughts and beleifs into rigourous mathematical frameworks has led to new insights

That said, we tend to deal with idealisd situtations (toy problems and scenarios) that are easier to deal with mathematically, but are are much more simple than real-world situations.

Another benefit of building a generalised mathematical framework is its results (if derived correctly) should be true whatever fancy new learning algorithm is the cutting edge in the future.





\draftnote{blue}{Chapter structure}{
	\begin{enumerate}
		\item Overview.
		\item Preliminaries.
		\item Discussion.
		\item Summary.
	\end{enumerate}
}






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{1Introduction/Old/main}
